Equalizer\\Programming and User Guide

### 2010-10-04 Developer/ProgrammingGuide/paper.tex
affinity WAR documentation update
[ ] May break build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.7.7 for Equalizer 0.9.1+svn\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.7.0   & Sep 09, 2009 & Updates based on hardcopy print\\
    1.7.1   & Oct 20, 2009 & Updates for new eq::GLWindow\\
    1.7.2   & Nov 18, 2009 & Add \sref{sSubpixel} and \sref{sFSAA} for Subpixel compounds\\
    1.7.3   & Feb 02, 2010 & Revision for Equalizer 0.9.1\\
    1.7.4   & Feb 22, 2010 & Add \sref{sSlaveCommit}\\
    1.7.5   & Jun 03, 2010 & Add \sref{sClusterSetup}\\
    1.7.6   & Aug 23, 2010 & General update for fabric changes\\
    1.7.7   & Oct 01, 2010 & SystemPipe and SystemWindow renaming\\
    \hline
  \end{tabularx}}
\clearpage

@@

@@

    attributes
    {
        hint_stereo         OFF | ON | AUTO
        hint_doublebuffer   OFF | ON | AUTO
        hint_decoration     OFF | ON
        hint_fullscreen     OFF | ON
        hint_swapsync       OFF | ON         # AGL, WGL only
        hint_drawable       window | pbuffer | FBO
        hint_statistics     off | fastest [on] | nicest
        planes_color        unsigned | RGBA16F | RGBA32F
        planes_alpha        unsigned
        planes_depth        unsigned
        planes_stencil      unsigned
        planes_accum        unsigned
        planes_accum_alpha  unsigned
        planes_samples      unsigned
    }

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications based on
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.7.8 for Equalizer 0.9.1+svn\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.7.0   & Sep 09, 2009 & Updates based on hardcopy print\\
    1.7.1   & Oct 20, 2009 & Updates for new eq::GLWindow\\
    1.7.2   & Nov 18, 2009 & Add \sref{sSubpixel} and \sref{sFSAA} for Subpixel compounds\\
    1.7.3   & Feb 02, 2010 & Revision for Equalizer 0.9.1\\
    1.7.4   & Feb 22, 2010 & Add \sref{sSlaveCommit}\\
    1.7.5   & Jun 03, 2010 & Add \sref{sClusterSetup}\\
    1.7.6   & Aug 23, 2010 & General update for fabric changes\\
    1.7.7   & Oct 01, 2010 & SystemPipe and SystemWindow renaming\\
    1.7.8   & Oct 04, 2010 & Document GPU affinity workaround hint\\
    \hline
  \end{tabularx}}
\clearpage

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_AFFINITY\\
  \textbf{Value} & OFF \textbar \ ON \textbar \ AUTO\textbar \ EXTERN\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines how the window handles the affinity context (WGL
  only). This hint is a workaround for NVidia drivers greater than 200, which
  contain a faulty implementation of the WGL\_NV\_gpu\_affinity extension. When
  set to AUTO, the hint is interpreted like EXTERN for windows and pbuffers with
  these drivers, in all other cases it is interpreted like ON. When set to ON,
  an affinity DC is used for all drawable types. When set to EXTERN, a normal DC
  is used to create the drawable, but an affinity DC is created and can be used
  by the application to render into a FBO. This hint may be ignored in later
  versions of Equalizer, once this workaround has become obsolete.\\
\end{tabularx}\\\vfill

@@

    attributes
    {
        hint_affinity       OFF | ON | AUTO | EXTERN
        hint_stereo         OFF | ON | AUTO
        hint_doublebuffer   OFF | ON | AUTO
        hint_decoration     OFF | ON
        hint_fullscreen     OFF | ON
        hint_swapsync       OFF | ON         # AGL, WGL only
        hint_drawable       window | pbuffer | FBO
        hint_statistics     off | fastest [on] | nicest
        planes_color        unsigned | RGBA16F | RGBA32F
        planes_alpha        unsigned
        planes_depth        unsigned
        planes_stencil      unsigned
        planes_accum        unsigned
        planes_accum_alpha  unsigned
        planes_samples      unsigned
    }
